Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-02-02 manuscriptPNAS.Rmd
Reformatted for PNAS.

---
title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
author: "Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker"
date: "Department of Psychology, University of York, UK"
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  pdf_document:
    toc: no
  word_document: default
  html_document: default
bibliography: references.bib
csl: elife.csl
---

@@

@@

@@

# Author contributions

**Federico Segala**: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review & editing, visualization. **Aurelio Bruno**: Conceptualization, writing - review & editing, supervision, project administration, funding acquisition. **Myat Aung**: Software, resources, writing - review & editing. **Alex Wade**: Conceptualization, methodology, resources, writing - review & editing, supervision, project administration, funding acquisition. **Daniel Baker**: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review & editing, visualization, supervision, project administration, funding acquisition.

# Declaration of interests

The authors declare no competing interests.

>>>>

---
title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
author: "Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker"
date: "Department of Psychology, University of York, UK"

output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  pdf_document:
    toc: no
  word_document: default
  html_document: default
bibliography: references.bib
csl: pnas.csl
---

@@

```
Federico G. Segala
**Email**: fgs502@york.ac.uk

**Author contributions: Federico Segala**: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review & editing, visualization. **Aurelio Bruno**: Conceptualization, writing - review & editing, supervision, project administration, funding acquisition. **Myat Aung**: Software, resources, writing - review & editing. **Alex Wade**: Conceptualization, methodology, resources, writing - review & editing, supervision, project administration, funding acquisition. **Daniel Baker**: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review & editing, visualization, supervision, project administration, funding acquisition.

**Competing interest declaration:** The authors declare no competing interests.

**Classification:** Biological Sciences - Neuroscience/Psychological and Cognitive Sciences

**Keywords:** Pupillary light reflex; Pupillometry; EEG; Pupil diameter; Binocular vision; Binocular interactions; Contrast matching; Computational modelling; Psychophysics

@@

# Significance Statement
Please note that it should not exceed 120 words, but should be at least 50 words in length.

@@
